\documentclass{article}


\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Software Requirements Specification (SRS) Upark}


\begin{document}
\maketitle


\section{Introduction}

\subsection {Document Objective}
This document establishes the functional and non-functional requirements for the development and implementation of the Parking Access Control System for the Technological University of Tijuana (UTT).

\subsection {Project Scope}
The system will address the automation of vehicle registration, the development of a web interface for checkpoint guards, and quick information retrieval to improve parking management and security.

\section{Functional Requirements}

\subsection{Vehicle Registration Automation}
Student Registration: Develop a platform that allows the systematic registration of vehicles associated with UTT students, including information such as names, license plates, models, and years of automobiles.

\subsection{Development of a Web Interface for Checkpoint Guards}
Intuitive Interface: Create an intuitive and user-friendly web interface for checkpoint guards.
Access to Detailed Information: Allow checkpoint guards to access detailed information about vehicles and owners before authorizing access to the parking lot.

\subsection{Quick Information Retrieval}
Efficient Search: Facilitate quick and effective searches for information on specific vehicles and owners for checkpoint guards.



\section{Non-Functional Requirements}

\subsection{Security}
Access Verification: Implement a secure access verification mechanism to reduce the risk of unauthorized entries.

\subsection{Performance}
Quick Response: Ensure a quick system response, especially during real-time information queries.

\subsection{Usability}
Intuitive Interface: Ensure that the web interface is intuitive and easy to use for checkpoint guards.

\section{Context and Justification}

\subsection{Objective of Database Knowledge Extraction}
Data Conversion: Perform knowledge extraction in the database to convert stored data into valuable and meaningful information.

\subsection{Motivation}
Enhanced Security: Strengthen parking lot security by implementing an access control system.
Improved Decision Making: Facilitate informed decision-making for checkpoint guards.

\section{Issues or Needs}
\subsection{Problem Identification}
Current Issues: Address identified issues in the current parking management system.


\section{Applications}
\subsection{Service Customization}
Personalized Recommendations: Provide personalized services to users based on historical patterns
\subsection{Technological Modernization}
License Plate Recognition: Implement advanced technologies, such as license plate recognition, to modernize parking services.

\subsection{Enhanced Security}
Access Control: Strengthen parking lot security through access control and license plate recognition.

\end{document}
